Event History Analysis for psychological time-to-event data: A tutorial in R with examples in Bayesian and frequentist workflows

### 2025-07-08 manuscript/manuscript.Rmd
add reference to Frank et al., 2025

To make causal inferences from the parameter estimates in model M1i, we first plot the densities of the draws from the posterior distributions of its population-level parameters in Figure 3, together with point (median) and interval estimates (80% and 95% credible intervals). A credible interval is a range of values that contains a parameter's true value with a specified probability, given the observed data and model.

>>>>

To make causal inferences from the parameter estimates in model M1i [@experimentology2025], we first plot the densities of the draws from the posterior distributions of its population-level parameters in Figure 3, together with point (median) and interval estimates (80% and 95% credible intervals). A credible interval is a range of values that contains a parameter's true value with a specified probability, given the observed data and model.

### 2025-07-08 manuscript/manuscript.tex
add reference to Frank et al., 2025

To make causal inferences from the parameter estimates in model M1i, we first plot the densities of the draws from the posterior distributions of its population-level parameters in Figure 3, together with point (median) and interval estimates (80\% and 95\% credible intervals). A credible interval is a range of values that contains a parameter's true value with a specified probability, given the observed data and model.

@@

>>>>

To make causal inferences from the parameter estimates in model M1i (Frank et al., 2025), we first plot the densities of the draws from the posterior distributions of its population-level parameters in Figure 3, together with point (median) and interval estimates (80\% and 95\% credible intervals). A credible interval is a range of values that contains a parameter's true value with a specified probability, given the observed data and model.

@@

\bibitem[\citeproctext]{ref-experimentology2025}
Frank, M. C., Braginsky, M., Cachia, J., Coles, N. A., Hardwicke, T. E., Hawkins, R. D., \ldots{} Williams, R. (2025). \emph{{Experimentology: An Open Science Approach to Experimental Psychology Methods}}. Stanford University. \url{https://doi.org/10.25936/3JP6-5M50}
